Gammapy: A Python package for gamma-ray astronomy

### 2023-03-22 src/ms-review.tex
Fix some references
Signed-off-by: Bruno Khélifi <khelifi@in2p3.fr>

\begin{figure*}[t]
	\centering
	\includegraphics[width=\textwidth]{figures/big-picture.pdf}
	\caption{
		Core idea and relation of \gammapy to different \gammaray instruments
		and the gamma astro data format (GADF). The top left shows the
		group of current and future pointing instruments based on the 
		imaging atmospheric Cherenkov technique (IACT). This includes
		instruments such as the Cherenkov Telescope Array Observatory (CTAO),
		the High Energy Stereoscopic System (H.E.S.S.), the
		Major Atmospheric Gamma Imaging Cherenkov Telescopes (MAGIC),
		and the Very Energetic Radiation Imaging Telescope Array System (VERITAS).
		The lower left shows the group of all-sky instruments such as the
		Fermi Large Area Telescope (Fermi-LAT) and the High Altitude
		Water Cherenkov Observatory (HAWC). The calibrated data of all those
		instruments can be converted and stored into the common GADF data format.
		\gammapy can read data stored in the GADF format.
		The \gammapy package is a community-developed project that
		provides a common interface to the data and analysis of all
		these \gammaray instruments. This way users can also easily combine data from
		different instruments and perform a joint analysis.
		\gammapy is built on the scientific Python ecosystem, and the required dependencies
		are shown below the \gammapy logo.
	}
	\label{fig:big_picture}

@@

The models follow a naming scheme which contains the category as a suffix to
the class name. The spectral models include a special class of normed models,
named using the \code{NormSpectralModel} suffix.
These spectral models feature a dimension-less \textit{norm} parameter
instead of an \textit{amplitude} parameter with physical units. They
can be used as an energy-dependent multiplicative correction
factor to another spectral model. They are typically used for
adjusting template-based models, or, for example, to take into account
the absorbtion effect on \gammaray spectra caused by the extra-galactic background
light (EBL) (\code{EBLAbsorptionNormSpectralModel}). \gammapy supports a variety
of EBL absorption models, such as those from \cite{Franceschini2008}, \cite{Finke2010},
and \cite{Dominguez2011}.

@@

%% CN: a link to the model gallery?
The model gallery provides a visual overview of the available models in
\gammapy. Most of the analytic models commonly used in \gammaray astronomy are
built-in. We also offer a wrapper to radiative models implemented in the Naima
package~\citep{naima}. The modelling framework can be easily extended with
user-defined models. For example, the radiative models of jetted Active Galactic Nuclei (AGN)
implemented in \agnpy, can be wrapped into \gammapy~\citep[see Section 3.5 of ][]{2022A&A...660A..18N}.

@@

\subsection{Broadband SED Modelling}
\label{ssec:broadband-sed-modeling}
By combining \gammapy with astrophysical modelling codes, users can also fit
astrophysical spectral models to \gammaray data. 
There are several Python packages that are able to model
the \gammaray emission, given a physical scenario. Among those
packages are Agnpy~\citep{agnpy}, Naima~\citep{naima}, Jetset~\citep{jetset}
and Gamera~\citep{gamera}.
Typically those emission models predict broadband emission from
radio, up to very high-energy \gammarays.
By relying on the multiple dataset types in \gammapy those
data can be combined to constrain such a broadband emission model.
\gammapy provides a built-in \code{NaimaSpectralModel} that allows
users to wrap a given astrophysical emission model from the
Naima package and fit it directly to \gammaray data.

@@

The increase in sensitivity and resolution provided by the new generation of
instruments scales up the number of detectable sources and the complexity of 
models needed to represent them accurately. As an example, if we compare the
results of the HGPS to the expectations from the \cta Galactic Plane survey
simulations, we jump from 78 sources detected by \hess to about 500 detectable by
CTA~\citep{2021arXiv210903729R}. This large increase in the amount of data to analyse
and increase in complexity of modelling scenarios, requires the high-level
analysis software to be both scalabale as well as performant.

>>>>

\begin{figure*}[t]
	\centering
	\includegraphics[width=\textwidth]{figures/big-picture.pdf}
	\caption{
		Core idea and relation of \gammapy to different \gammaray instruments
		and the gamma astro data format (GADF). The top left shows the
		group of current and future pointing instruments based on the 
		imaging atmospheric Cherenkov technique (IACT). This includes
		instruments such as the Cherenkov Telescope Array Observatory (CTAO),
		the High Energy Stereoscopic System (H.E.S.S.), the
		Major Atmospheric Gamma Imaging Cherenkov Telescopes (MAGIC),
		and the Very Energetic Radiation Imaging Telescope Array System (VERITAS).
		The lower left shows the group of all-sky instruments such as the
		Fermi Large Area Telescope (\textit{Fermi}-LAT) and the High Altitude
		Water Cherenkov Observatory (HAWC). The calibrated data of all those
		instruments can be converted and stored into the common GADF data format.
		\gammapy can read data stored in the GADF format.
		The \gammapy package is a community-developed project that
		provides a common interface to the data and analysis of all
		these \gammaray instruments. This way users can also easily combine data from
		different instruments and perform a joint analysis.
		\gammapy is built on the scientific Python ecosystem, and the required dependencies
		are shown below the \gammapy logo.
	}
	\label{fig:big_picture}

@@

The models follow a naming scheme which contains the category as a suffix to
the class name. The spectral models include a special class of normed models,
named using the \code{NormSpectralModel} suffix.
These spectral models feature a dimension-less \textit{norm} parameter
instead of an \textit{amplitude} parameter with physical units. They
can be used as an energy-dependent multiplicative correction
factor to another spectral model. They are typically used for
adjusting template-based models, or, for example, to take into account
the absorbtion effect on \gammaray spectra caused by the extra-galactic background
light (EBL) (\code{EBLAbsorptionNormSpectralModel}). \gammapy supports a variety
of EBL absorption models, such as those from \cite{Franceschini2008, Franceschini2017}, \cite{Finke2010},
and \cite{Dominguez2011}.

@@

%% CN: a link to the model gallery?
The model gallery provides a visual overview of the available models in
\gammapy. Most of the analytic models commonly used in \gammaray astronomy are
built-in. We also offer a wrapper to radiative models implemented in the Naima
package~\citep{naima}. The modelling framework can be easily extended with
user-defined models. For example, the radiative models of jetted Active Galactic Nuclei (AGN)
implemented in \agnpy~\citep{agnpy2022}, can be wrapped into 
\gammapy~\citep[see Section 3.5 of ][]{2022A&A...660A..18N}.

@@

\subsection{Broadband SED Modelling}
\label{ssec:broadband-sed-modeling}
By combining \gammapy with astrophysical modelling codes, users can also fit
astrophysical spectral models to \gammaray data. 
There are several Python packages that are able to model
the \gammaray emission, given a physical scenario. Among those
packages are Agnpy~\citep{agnpy2022}, Naima~\citep{naima}, Jetset~\citep{jetset}
and Gamera~\citep{gamera}.
Typically those emission models predict broadband emission from
radio, up to very high-energy \gammarays.
By relying on the multiple dataset types in \gammapy those
data can be combined to constrain such a broadband emission model.
\gammapy provides a built-in \code{NaimaSpectralModel} that allows
users to wrap a given astrophysical emission model from the
Naima package and fit it directly to \gammaray data.

@@

The increase in sensitivity and resolution provided by the new generation of
instruments scales up the number of detectable sources and the complexity of 
models needed to represent them accurately. As an example, if we compare the
results of the HGPS to the expectations from the \cta Galactic Plane survey
simulations, we jump from 78 sources detected by \hess to about 500 detectable by
CTA~\citep{Remy2021}. This large increase in the amount of data to analyse
and increase in complexity of modelling scenarios, requires the high-level
analysis software to be both scalabale as well as performant.
